Understanding Characteristics of Popular Streamers on Live Streaming Platforms: Evidence from Twitch.tv 

* [Zhao et al (2020 )](https://papers.ssrn.com/sol3/papers.cfm?abstract_id=3388949)

---
class: inverse, center, middle
# Characteristics of Popular Streamers

---
class: font160
# Motivation

**Strategic Question**: What are the key characteristics of popular streamers

* Streamers as an insight into influencers more generally ...

**Why relevant**:

* *Influencer*: Can you "become" more popular?
* *Firms*: What are characteristics of influencers that get high engagement?  

**Observational Study + no "clever" empirical strategy**

$\implies$ **Findings are descriptive**

---
class: font120
# Research Hypotheses

```{r, echo = FALSE, fig.align = "center", out.width="65%"}
url <- "figs/influencer_charac_hypotheses.png"
knitr::include_graphics(url)
```

**Affordance?** In this paper...

* Profile Information & social interactivity

... as **distinct from professionalism** ... 

* Part of a professional team & gaming proficiency

---
class: font160
# Data

516 Twitch streamers over three weeks

**Streamer Popularity** (static!): 

* View count
* Number of followers

**Social Interactivity**: 

* Webcam
* Words in Transcript 
* Links to Twitter Profile 

**Personality Traits**:  

* Linguistic Analyses of stream transcripts & tweets

---
# Measurement

```{r, echo = FALSE, fig.align = "center", out.width="70%"}
url <- "figs/influencer_charac_measurement.png"
knitr::include_graphics(url)
```

---
class: font150
# Regression

Regression equation:

```{r, echo = FALSE, fig.align = "center", out.width="80%"}
url <- "figs/influencer_charac_regression.png"
knitr::include_graphics(url)
```

.center[.font70[Note the lack of subscripts! Don't be **that** person!]]

Remarks:

* PBA: Profile Building Affordance 
* Same regression with no. of followers as alternative outcome

---
# Results

```{r, echo = FALSE, fig.align = "center", out.width="70%"}
url <- "figs/influencer_charac_results_main.png"
knitr::include_graphics(url)
```

**Remark**: Mind the overly causal language in the results section of the paper

---
class: font160
# Takeaways

Having:

* Profile Descriptors 
* Camera On 
* Talking to your viewers 
* Being a Professional 

**positively associated** with being more **popular** on Twitch 

**Personality Trait** results are **mixed** ... 

* Openness and conscientiousness negative associated with popularity 
* Neuroticism positively associated

(**my** worries on this bit: Omitted Variables, measurement errors)