Understanding Characteristics of Popular Streamers on Live Streaming Platforms: Evidence from Twitch.tv 

* [Zhao et al (2020 )](https://papers.ssrn.com/sol3/papers.cfm?abstract_id=3388949)

---
class: inverse, center, middle
# Characteristics of Popular Streamers

---
class: font160
# Motivation

**Strategic Question**: What are the key characteristics of popular streamers

* Streamers as an insight into influencers more generally ...

**Why relevant**:

* *Influencer*: Can you "become" more popular?
* *Firms*: What are characteristics of influencers that get high engagement?  

**Observational Study + no "clever" empirical strategy**

$\implies$ **Findings are descriptive**

---
class: font120
# Research Hypotheses

```{r, echo = FALSE, fig.align = "center", out.width="65%"}
url <- "figs/influencer_charac_hypotheses.png"
knitr::include_graphics(url)
```

**Affordance?** In this paper...

* Profile Information & social interactivity

... as **distinct from professionalism** ... 

* Part of a professional team & gaming proficiency

---
class: font160
# Data

516 Twitch streamers over three weeks

**Streamer Popularity** (static!): 

* View count
* Number of followers

**Social Interactivity**: 

* Webcam
* Words in Transcript 
* Links to Twitter Profile 

**Personality Traits**:  

* Linguistic Analyses of stream transcripts & tweets

---
# Measurement

```{r, echo = FALSE, fig.align = "center", out.width="70%"}
url <- "figs/influencer_charac_measurement.png"
knitr::include_graphics(url)
```

---
class: font150
# Regression

Regression equation:

```{r, echo = FALSE, fig.align = "center", out.width="80%"}
url <- "figs/influencer_charac_regression.png"
knitr::include_graphics(url)
```

.center[.font70[Note the lack of subscripts! Don't be **that** person!]]

Remarks:

* PBA: Profile Building Affordance 
* Same regression with no. of followers as alternative outcome

---
# Results

```{r, echo = FALSE, fig.align = "center", out.width="70%"}
url <- "figs/influencer_charac_results_main.png"
knitr::include_graphics(url)
```

**Remark**: Mind the overly causal language in the results section of the paper

---
class: font160
# Takeaways

Having:

* Profile Descriptors 
* Camera On 
* Talking to your viewers 
* Being a Professional 

**positively associated** with being more **popular** on Twitch 

**Personality Trait** results are **mixed** ... 

* Openness and conscientiousness negative associated with popularity 
* Neuroticism positively associated

(**my** worries on this bit: Omitted Variables, measurement errors)

---
class: inverse, center, middle
# What is the effect of sponsorship disclosure on influencers?

---
class: font160
# Motivation 

**Strategic Question**: How does sponsorship disclosure impact consumer evaluations of brands and influencers?

* And does it differ across influencer type?

**Why Relevant?**

* Sponsored influencer posts used to be the "wild west" of advertising
  * i.e. unregulated, left to consumers to discern 
  * Unlike most advertising markets
* Increase regulation mandated by governments ...
* ... But actual uptake is still low

**Application**: a Lab Experiment (Why?)

---
class: font140
# Conceptual Framework

```{r, echo = FALSE, fig.align = "center", out.width="80%"}
url <- "figs/disclosure_conceptual.png"
knitr::include_graphics(url)
```

---
class: font140
# Experiments: An Overview

**Study 1a**: Influencer Type on persuasion knowledge and trustworthiness? 
  * What are the impacts on brand evaluation and influencer likeability?

**Study 1b**: Replicates Study 1a with "more control"

* Less info about influencer changing simultaneously
* (Won't discuss this here)

**Study 2**: What does **disclosure vs non-disclosure** do? 

**Study 3**: Replicates Study 2 with real influencers
* (Won't discuss this here)

---
class: font150
# Study 1a

The Basics: 

* **Fictitious** influencers 

* Influencer **Types**: Nano, micro, macro, mega, nano

* Industry: **Food, Instagram** 

* Participants: 282 Western Europeans

---
class: font130
# Study 1a: Stimuli

Varies **Profile info** across types of influencer 

```{r, echo = FALSE, fig.align = "center", out.width="80%"}
url <- "figs/disclosure_study_1_manip1.png"
knitr::include_graphics(url)
```

Varies **likes** across types of influencer 


```{r, echo = FALSE, fig.align = "center", out.width="70%"}
url <- "figs/disclosure_study_1_manip2.png"
knitr::include_graphics(url)
```

---
# Study 1a: Results 

```{r, echo = FALSE, fig.align = "center", out.width="55%"}
url <- "figs/disclosure_study_1_results.png"
knitr::include_graphics(url)
```

**Takeaways**: 

* Mediation via persuasion knowledge for macro, mega, nano 
* No Mediation via trustworthiness of the post 

Persuasion Knowledge?

* Consumers expected post to be sponsored

$\implies$ when consumers think something is sponsored and can't be verified perceptions go down

---
class: font150
# Study 2 

**2 x 2 design**: 

* Nano vs Mega 
* Non-disclosure vs disclosure 

```{r, echo = FALSE, fig.align = "center", out.width="50%"}
url <- "figs/disclosure_study_2_manip.png"
knitr::include_graphics(url)
```

---
class: font140
# Study 2: Results 

```{r, echo = FALSE, fig.align = "center", out.width="50%"}
url <- "figs/disclosure_study_2_results_fig.png"
knitr::include_graphics(url)
```

* If no disclosure, when respondant thinks post is sponsored their trust in post content falls
  * Leads to lower evals of influencer and brand (not shown)
* **NOT** the case when sponsorship is disclosed

---
class: font160
# Takeaways 

* Revealing a post is **sponsored** makes **consumers trust the post more**, particularly **when the content is perceived to be sponsored**

* ... **Prevents decrease in likeability of influencers** and **negative brand evaluations** 