Understanding Characteristics of Popular Streamers on Live Streaming Platforms: Evidence from Twitch.tv 

* [Zhao et al (2020 )](https://papers.ssrn.com/sol3/papers.cfm?abstract_id=3388949)

---
class: inverse, center, middle
# Characteristics of Popular Streamers

---
class: font160
# Motivation

**Strategic Question**: What are the key characteristics of popular streamers

* Streamers as an insight into influencers more generally ...

**Why relevant**:

* *Influencer*: Can you "become" more popular?
* *Firms*: What are characteristics of influencers that get high engagement?  

**Observational Study + no "clever" empirical strategy**

$\implies$ **Findings are descriptive**

---
class: font120
# Research Hypotheses

```{r, echo = FALSE, fig.align = "center", out.width="65%"}
url <- "figs/influencer_charac_hypotheses.png"
knitr::include_graphics(url)
```

**Affordance?** In this paper...

* Profile Information & social interactivity

... as **distinct from professionalism** ... 

* Part of a professional team & gaming proficiency

---
class: font160
# Data

516 Twitch streamers over three weeks

**Streamer Popularity** (static!): 

* View count
* Number of followers

**Social Interactivity**: 

* Webcam
* Words in Transcript 
* Links to Twitter Profile 

**Personality Traits**:  

* Linguistic Analyses of stream transcripts & tweets

---
# Measurement

```{r, echo = FALSE, fig.align = "center", out.width="70%"}
url <- "figs/influencer_charac_measurement.png"
knitr::include_graphics(url)
```

---
class: font150
# Regression

Regression equation:

```{r, echo = FALSE, fig.align = "center", out.width="80%"}
url <- "figs/influencer_charac_regression.png"
knitr::include_graphics(url)
```

.center[.font70[Note the lack of subscripts! Don't be **that** person!]]

Remarks:

* PBA: Profile Building Affordance 
* Same regression with no. of followers as alternative outcome

---
# Results

```{r, echo = FALSE, fig.align = "center", out.width="70%"}
url <- "figs/influencer_charac_results_main.png"
knitr::include_graphics(url)
```

**Remark**: Mind the overly causal language in the results section of the paper

---
class: font160
# Takeaways

Having:

* Profile Descriptors 
* Camera On 
* Talking to your viewers 
* Being a Professional 

**positively associated** with being more **popular** on Twitch 

**Personality Trait** results are **mixed** ... 

* Openness and conscientiousness negative associated with popularity 
* Neuroticism positively associated

(**my** worries on this bit: Omitted Variables, measurement errors)

---
class: inverse, center, middle
# What is the effect of sponsorship disclosure on influencers?

---
class: font160
# Motivation 

**Strategic Question**: How does sponsorship disclosure impact consumer evaluations of brands and influencers?

* And does it differ across influencer type?

**Why Relevant?**

* Sponsored influencer posts used to be the "wild west" of advertising
  * i.e. unregulated, left to consumers to discern 
  * Unlike most advertising markets
* Increase regulation mandated by governments ...
* ... But actual uptake is still low

**Application**: a Lab Experiment (Why?)

---
class: font140
# Conceptual Framework

```{r, echo = FALSE, fig.align = "center", out.width="80%"}
url <- "figs/disclosure_conceptual.png"
knitr::include_graphics(url)
```

---
class: font140
# Experiments: An Overview

**Study 1a**: Influencer Type on persuasion knowledge and trustworthiness? 
  * What are the impacts on brand evaluation and influencer likeability?

**Study 1b**: Replicates Study 1a with "more control"

* Less info about influencer changing simultaneously
* (Won't discuss this here)

**Study 2**: What does **disclosure vs non-disclosure** do? 

**Study 3**: Replicates Study 2 with real influencers
* (Won't discuss this here)

---
class: font150
# Study 1a

The Basics: 

* **Fictitious** influencers 

* Influencer **Types**: Nano, micro, macro, mega, nano

* Industry: **Food, Instagram** 

* Participants: 282 Western Europeans

---
class: font130
# Study 1a: Stimuli

Varies **Profile info** across types of influencer 

```{r, echo = FALSE, fig.align = "center", out.width="80%"}
url <- "figs/disclosure_study_1_manip1.png"
knitr::include_graphics(url)
```

Varies **likes** across types of influencer 


```{r, echo = FALSE, fig.align = "center", out.width="70%"}
url <- "figs/disclosure_study_1_manip2.png"
knitr::include_graphics(url)
```

---
# Study 1a: Results 

```{r, echo = FALSE, fig.align = "center", out.width="55%"}
url <- "figs/disclosure_study_1_results.png"
knitr::include_graphics(url)
```

**Takeaways**: 

* Mediation via persuasion knowledge for macro, mega, nano 
* No Mediation via trustworthiness of the post 

Persuasion Knowledge?

* Consumers expected post to be sponsored

$\implies$ when consumers think something is sponsored and can't be verified perceptions go down

---
class: font150
# Study 2 

**2 x 2 design**: 

* Nano vs Mega 
* Non-disclosure vs disclosure 

```{r, echo = FALSE, fig.align = "center", out.width="50%"}
url <- "figs/disclosure_study_2_manip.png"
knitr::include_graphics(url)
```

---
class: font140
# Study 2: Results 

```{r, echo = FALSE, fig.align = "center", out.width="50%"}
url <- "figs/disclosure_study_2_results_fig.png"
knitr::include_graphics(url)
```

* If no disclosure, when respondant thinks post is sponsored their trust in post content falls
  * Leads to lower evals of influencer and brand (not shown)
* **NOT** the case when sponsorship is disclosed

---
class: font160
# Takeaways 

* Revealing a post is **sponsored** makes **consumers trust the post more**, particularly **when the content is perceived to be sponsored**

* ... **Prevents decrease in likeability of influencers** and **negative brand evaluations** 

---
class: font160
# Today's Topic Coverage

Does volume or sentiment of online word of mouth matter for consumers?

* [Chintagunta, Gopinath & Venkataraman (2010)](https://pubsonline.informs.org/doi/pdf/10.1287/mksc.1100.0572)

* *Recent Updates*: Whats new in Online Word of Mouth research?
  * [Seiler, Yao & Zervas (2018)](https://songyao21.github.io/Research_Papers/WOM_book_chapter.pdf) 
  * [Deer, Chintagunta & Crawford (2022)](https://papers.ssrn.com/sol3/papers.cfm?abstract_id=4227912)

  ---
class: inverse, center, middle

# Does volume or sentiment of online word of mouth matter for consumers?

---
class: font160
# What is Word of Mouth Marketing?

Consumer's interest in a company's product or service is reflected in their "daily dialogues"

* Why is this *new* in "social media"?
  * It isn't a new idea ...
  * The "social web" with it's increasing connectivity makes it more salient
  * ... and measurable

---
class: font160
# Types of Word of Mouth 

**Organic word of mouth**:

* People become advocates for a product and have a desire to share their views.
* **This is our focus**

**Amplified word of mouth**: 

* Marketers launch campaigns designed to encourage or accelerate WoM in existing or new communities.
* We'll come back to this later in the course -- "Social Advertising"

*Lurking Issue:* Online versus Offline

* Distinction is always lurking in the background

---
class: font160
# Social Media Word of Mouth Matters

* Consumers now spend more than 135 mins per day on social media

* Social Media fostered growing importance of WoM marketing

* Chief Marketing Officers think online WoM matters
    - ... Rationalized by consumer's trust in online info from peers (Nielsen, 2013)
    - 64% of marketing executives believe word of mouth is the most effective form of marketing
    - Only 6% say they have mastered it.

---
class: font160
# Why Word of Mouth Might Matter

.center[
`r icons::fontawesome("question", style = "solid")` What reasons might word of mouth matter for consumers?
]


---
class: font160
# Why Word of Mouth Might Matter

Mechanisms at play:

1. Awareness
2. Buzz
3. Social learning
4. Consumption complementarities

Most often we see this operationalized as:

* Awareness & Buzz $\rightarrow$ **volume** of tweets
* Social learning $\rightarrow$ **sentiment** in tweet's text
  * Sentiment often called *valence*
* Consumption complementarities $\rightarrow$ *nothing*

---
class: font160
# Why Should Marketers Care?

- Social media can generate awareness, buzz and information diffusion that ultimately influences demand

<br>

- Important when:
    1. Relying on "hyped release strategies"
    2. Uncertainty about a product's quality

<br>

- Examples: movies, books, consumer electronics, video games, fashion

.center[**Most relevant for new products early in release**]

---
class: font160
# The paper...

**Strategic Question**: How does volume, valence and variance of online user reviews impact product demand? 

* Some definitions: 
  * **Online Word of Mouth**: user reviews on social media 
    * Thought of as different from star ratings 
  * **Valence** (aka *sentiment*): how positive / negative the reviews are

**Why relevant?** 

* Volume vs Valence effects are widely debated
* And (generally) hard to measure
* Relevant for new products, experience goods
  * Movie industry is a good laboratory for these products

---
class: font140
# Application: The Movie Industry

* Time period: November 2003 to February 2005

* Movies: 148 

* Yahoo! Movies discussion boards

* Opening weekend box office data across DMAs

* Why DMA level data important here? 
  1. Movies weren't always released across all of US on same day
  2. Allows different in OWoM metrics for the same movie on an "opening" weekend

**Why not an experiment?** 

* Experimental variation in volume and sentiment (almost) impossible
* Paper pre-dates the experimental revolution

---
# Variable Definitions 

```{r, echo = FALSE, fig.align = "center", out.width="100%"}
url <- "figs/cgv_data.png"
knitr::include_graphics(url)
```

---
# Regression Model 

**Regression Equation**: 

```{r, echo = FALSE, fig.align = "center", out.width="40%"}
url <- "figs/cgv_regression.png"
knitr::include_graphics(url)
```

$i$ is movie, $j$ is DMA (region)

**Coefficients of Interest**: $\gamma_1$, $\gamma_2$, $\gamma_3$

**Bells and Whistles (in method)**: 

* Endogeneity (offline vs online, omitted variables)
* Correlation in errors across markets

$\implies$ fix via Instrumental Variables + tweaks to standard error calculation you're used to

---
# Main Results 

```{r, echo = FALSE, fig.align = "center", out.width="80%"}
url <- "figs/cgv_main.png"
knitr::include_graphics(url)
```

**Valence is** statistically significant 

**Volume is not**

---
# Comparison to National Aggregation 

.center[**National Demand is what people "usually" do**]

```{r, echo = FALSE, fig.align = "center", out.width="60%"}
url <- "figs/cgv_national.png"
knitr::include_graphics(url)
```

**Valence is not** statistically significant , **Volume is**


---
class: font150
# Whats Causing this Difference? 

When we have **sequential** release of products

* Sentiment is "moving around more" than volume 
  * Why?
  * Pre-release volume >> post-release volume 
  * Can learn quality from consumers who have seen movie
* And sequential release was/is a strategic decision
  * In part due because firms want to leverage social learning

$\implies$ likely that we see sentiment effects

When we have **simultaneous** national release of products

* More variation in volume than sentiment 
* And sentiment is *noisy* for all products in the opening week

$\implies$ likely that we see volume effects

.font70[These thoughts are speculative on my part]

---
class: font160
# Takeaways from the paper

* Emphasizes the role of **valence** / **sentiment** of online reviews in influencing new product demand in experience goods markets 
  * In **contrast** to **volume**
  * Which is what previous studies emphasized

* Marketers should find ways to spread **positive** online WoM to boost demand 

---
class: font150
# Recent Developments I 

.center[
**Can we get experimental variation in volume and sentiment?**
]

* Maybe if there's a "Natural Experiment"
* Studied by [Seiler, Yao & Wang (2018)](https://pubsonline.informs.org/doi/abs/10.1287/mksc.2017.1045) 

**Setting**: Shutdown of Sina Weibo in mainland China & but not HK
* Industry: Existing TV shows 

**Findings**: 

* Volume not sentiment is significant
* Small elasticities, approx 0.02 
* Mechanism at play is consumption complementarities 

---
class: font140
# Recent Developments II

.center[
**How far to "believable" numbers can get get without experimental variation?** 

**Can we reconcile the volume vs sentiment debate?**
]

* If we can **control** for (almost) all the omitted variables
* Studied by [Deer, Crawford, Chintagunta (2022)](https://papers.ssrn.com/sol3/papers.cfm?abstract_id=4227912) 

**Setting**: US Movie Industry & Twitter WoM

**Findings**: 

* Distinguish Pre- vs Post- release volume and sentiment
* Volume **and** sentiment significant
* Small-ish volume elasticities, larger sentiment elasticities 
* Differs across **types** of movies
  *  Buzz: Franchise movies, 
  *  Awareness: (expected) mid-tier movies, 
  *  Social learning: (expected) small movies